### 2015-06-18 thesis-proposal/problem.tex
Fixed some missing things

More advanced dialects introduce new type structure, going beyond what is possible with derived syntax. Record types provide a simple example -- they cannot be expressed by context-independent elaboration to a language with only nullary and binary product types. Various  languages have explored ``record-like'' primitives that go still further, supporting functional update and extension operators, width and depth coercions (sometimes implicit)%\cite{Cardelli:1984:SMI:1096.1098}
, methods, prototypic dispatch and other ``semantic embellishments'' that cannot be expressed by context-independent elaboration to a language with only standard record types (we will detail an  example in Sec. \ref{sec:metamodules}). OCaml primitively builds in the type structure of ``polymorphic variants'', ``open datatypes'' and  operations that use format strings like $\mathtt{sprintf}$ \cite{ocaml-manual}. ReactiveML builds in primitives for functional reactive programming \cite{mandel2005reactiveml}. ML5 builds in high-level primitives for distributed programming based on a modal lambda calculus \cite{Murphy:2007:TDP:1793574.1793585}. Manticore \cite{conf/popl/FluetRRSX07} and AliceML  \cite{AliceLookingGlass} build in parallel programming primitives with a more elaborate type structure than is found in their respective core calculi. 
MLj builds in the type structure of the Java object system (motivated by a desire to interface safely and naturally with Java libraries) \cite{Benton:1999:IWW:317636.317791}. Other dialects do the same for other foreign languages, e.g. Furr and Foster describe a dialect of OCaml that builds in the type structure of C \cite{Furr:2005:CTS:1065010.1065019}. Tools like proof assistants and logical frameworks are used to specify and reason metatheoretically about dialects like these, and tools like compiler generators and language frameworks \cite{erdweg2013state} lower their implementation cost, again contributing to their proliferation.

>>>>

More advanced dialects introduce new type structure, going beyond what is possible with derived syntax. Record types provide a simple example -- they cannot be expressed by context-independent elaboration to a language with only nullary and binary product types. Various  languages have explored ``record-like'' primitives that go still further, supporting functional update and extension operators, width and depth coercions (sometimes implicit)%\cite{Cardelli:1984:SMI:1096.1098}
, methods, prototypic dispatch and other ``semantic embellishments'' that cannot be expressed by context-independent elaboration to a language with only standard record types (we will detail an  example in Sec. \ref{sec:metamodules}). OCaml primitively builds in the type structure of ``polymorphic variants'', ``open datatypes'' and  operations that use format strings like $\mathtt{sprintf}$ \cite{ocaml-manual}. ReactiveML builds in primitives for functional reactive programming \cite{mandel2005reactiveml}. ML5 builds in high-level primitives for distributed programming based on a modal lambda calculus \cite{Murphy:2007:TDP:1793574.1793585}. Manticore \cite{conf/popl/FluetRRSX07} and AliceML  \cite{AliceLookingGlass} build in parallel programming primitives with a more elaborate type structure than is found in core calculi for parallel programming. 
MLj builds in the type structure of the Java object system (motivated by a desire to interface safely and naturally with Java libraries) \cite{Benton:1999:IWW:317636.317791}. Other dialects do the same for other foreign languages, e.g. Furr and Foster describe a dialect of OCaml that builds in the type structure of C \cite{Furr:2005:CTS:1065010.1065019}. Tools like proof assistants and logical frameworks are used to specify and reason metatheoretically about dialects like these, and tools like compiler generators and language frameworks \cite{erdweg2013state} lower their implementation cost, again contributing to their proliferation.
